Generate data for multispecies modeling, including diet!

### 2020-09-17 NOBAmsdiets.Rmd
test multi-survey wrapper

## Generating the dataset 
*(PLACEHOLDER; not done yet June 19 2020)*

@@

```{r, code = readLines("./config/NOBA2Config.R"), eval=F}
```

@@

```{r, code = readLines("./config/omdimensions.R"), eval=F}
```

`mssurvey_spring.R` and `mssurvey_fall.R` configure the fishery independent surveys:

```{r, code = readLines("./config/mssurvey_spring.R"), eval=F}
```

```{r, code = readLines("./config/mssurvey_fall.R"), eval=F}
```

@@

```{r, code = readLines("./config/msfishery.R"), eval=F}
```

@@

NOBAom_ms_ind <- om_index(usersurvey = here("config/mssurvey.R"), 
                           userfishery = here("config/msfishery.R"),
                           omlist_ss = NOBAom_ms, 
                           n_reps = 1, 
                           save = TRUE)

NOBAom_ms_comp <- om_comps(usersurvey = here("config/mssurvey.R"), 
                           userfishery = here("config/msfishery.R"),
                           omlist_ss = NOBAom_ms, 
                           n_reps = 1, 
                           save = TRUE)

@@

omlist_ss <- NOBAom_cod
source(here("config/omdimensions.R"))

#read time series data
survObsBiom <- readRDS(file.path(d.name, paste0(scenario.name, "surveyB.rds")))

survObsBiom <- survObsBiom[[1]]

>>>>

## Generating the dataset (September 2020)

@@

```{r, code = readLines("./config/NOBA2Config.R")}
```

@@

```{r, code = readLines("./config/omdimensions.R")}
```

`mssurvey_spring.R` and `mssurvey_fall.R` configure the fishery independent surveys (in this test, surveys sample all model polygons in all years and have efficiency of 1 for all species, with no size selectivity):

```{r, code = readLines("./config/mssurvey_spring.R")}
```

```{r, code = readLines("./config/mssurvey_fall.R")}
```

@@

```{r, code = readLines("./config/msfishery.R")}
```

@@

# new wrapper for multiple surveys saves survey output separately
# but returns a list with all surveys, not ideal; make consistent

NOBAom_ms_ind <- om_index(usersurvey = c(here("config/mssurvey_spring.R"), 
                                         here("config/mssurvey_fall.R")), 
                           userfishery = here("config/msfishery.R"),
                           omlist_ss = NOBAom_ms, 
                           n_reps = 1, 
                           save = TRUE)

NOBAom_ms_comp <- om_comps(usersurvey = c(here("config/mssurvey_spring.R"), 
                                         here("config/mssurvey_fall.R")), 
                           userfishery = here("config/msfishery.R"),
                           omlist_ss = NOBAom_ms, 
                           n_reps = 1, 
                           save = TRUE)

@@

omlist_ss <- NOBAom_ms
source(here("config/omdimensions.R"))

#read time series data--now needs survey name from config files
survname <- c("BTS_spring_allbox_effic1", "BTS_fall_allbox_effic1")

#need plotting/visualization wrappers
#survObsBiom <- readRDS(file.path(d.name, paste0(scenario.name, "surveyB.rds")))

survObsBiom <- NOBAom_ms$survObsBiom[[survname]]
